---
title: "Usage of *techbios* package"
author: "John Horton & Alexander Gedranovich"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Demo usage of *techbios* package}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

Tools for working with LinkedIn biographical data for people working in tech, namely Stanford CS degree holders for use "A Theory of Silicon Valley"

# Installation

Type in `R` console:

```{r eval = FALSE}
install.packages("devtools")
devtools::install_github("johnjosephhorton/techbios",
                         build_vignettes = TRUE)
```

# Usage

## Load the library

```{r, message=FALSE}
library(techbios)
```

Package `techbios` has several solution around Stanford PhD graduates data. They are accessible via pre-calculated data.

## Q1: Number of Stanford PhD graduates by year

```{r fig.height=5, fig.width=7}
# Shows data
data(df_1)
head(df_1)

# Plots data
StanfordCSPhDGradsPerYear()
```


## Q2: Fraction of Stanford CS PhD grads choosing various career options over time

```{r fig.height=5, fig.width=7}
# Shows data
data(df_2)
head(df_2)

# Plots data
StanfordCSPhDGradsOccChoicePerYear()
```


## Q3: Career trajectories

```{r fig.height=5, fig.width=7}
# Plots data
StanfordCSPhDGradsCareerHistories()
```

